\documentclass[main.tex]{subfiles}
\begin{document}
\maketitle


\setexercise{1}{3}{3}
\begin{exercise}
Find an example to show that the objects and morphisms in the image of a functor $F \colon \sC\to\sD$ do not necessarily define a subcategory of $\sD$.
\end{exercise}

At first, I was suspicious of this exercise since it seemed to me that the proof that the image of a group (or monoid, or ring, \dots) homomorphism is a subgroup (or submonoid, or subring, \dots) carries through without any change. Perhaps the author meant for the exercise to be something different?

So, I asked her, and she pointed out a straightforward example that also exposed the error in my reasoning. I will give below a simplification of the example that she sent me. First, here is the error in my original argument.

Let $a$ and $b$ be morphisms in the image of $F$ such that $\dom a=\cod b$ so that we can form $ab$ in $\sD$. Since $a$ and $b$ are in the image of $F$, there are morphisms $f$ and $g$ in $
\sC$ such that $a=Ff$ and $b=Fg$. Then 
$$ab=FfFg=F(fg)$$
so that $ab$ is in the image of $F$. 

Right? Wrong!! In order to compose $f$ and $g$ we need that $\dom f=\cod g$. All we know for sure is that $\dom Ff=\cod Fg$. If $F$ is injective on objects, then the argument above is valid. But perhaps $F$ is not injective.

\begin{center}{\bf The Example.}\end{center}
Now, I provide the example requested in this exercise. Let $\sC={\mathbb 2}$ be the ordinal category pictured as so:
\[\xymatrix{0\ar[r]^f&1.}\]
Let $g$ be an endomorphism of some object $x$ in some category $\sD$ such that 
$gg$ is equal to neither $1_x$ nor $g$. For example, we could take $x$ to be 
the unique object in $B\NN$ and $g=3$. Composition of morphisms in $B\NN$ is 
addition in $\NN$  so that $gg=g+g=6\ne 3,0$.

Then we have a functor $F:{\mathbb 2}\rightarrow\sD$ given by $F0=F1=x$, 
$F1_0=F1_1=1_x$ and $Ff=g$. There are only four possible compositions of the 
three morphisms in ${\mathbb 2}$, $1_01_0$, $f1_0$, $1_1f$ and $1_11_1$ and it 
is easy to see that $F$ preserves all four of these compositions. Thus, $F$ is 
a functor.

However, the image of $F$ has only the two morphisms $1_x$ and $g$. Since $gg$ is not in the image, the image of $F$ is not a subcategory of $\sD$.

\end{document}
