\documentclass[../../main]{subfiles}
\begin{document}

\paragraph{}
\begin{center}
\end{center}

\begin{exercise}
	Finish the following proof of Lemma 1.5.10:
\end{exercise}

\settheorem{1}{5}{10}
\begin{lemma}
	Any morphism \(f\colon a\to b\) and fixed isomorphisms \(a \cong a'\) and
	\(b \cong b'\) determine a unique morphism \(f'\colon a'\to b'\) so that any
	of---or, equivalently, all of---the following four diagrams commute:
	\[\xymatrix{
	a\ar[d]_{f} & a'\ar[l]_{\cong}\ar[d]^{f'} &
	a\ar[d]_{f}\ar[r]^{\cong} & a'\ar[d]^{f'} &
	a\ar[d]_{f} & a'\ar[l]_{\cong}\ar[d]^{f'} &
	a\ar[d]_{f}\ar[r]^{\cong} & a'\ar[d]^{f'} \\
	b\ar[r]_{\cong} & b' &
	b\ar[r]_{\cong} & b' &
	b & b'\ar[l]^{\cong} &
	b & b'\ar[l]^{\cong}
	}\]
	% The first diagram defines \(f'\). The commutativity of the remaining diagrams
	% will be proven below.
\end{lemma}
\popthm

For legibility, I use \(\alpha\) to denote the isomorphism
\(\cong\colon a'\to a\) (with \(\alpha^{-1}\) denoting its inverse) and
\(\beta\) to denote the isomorphism \(\cong\colon b'\to b\) (with
\(\beta^{-1}\) denoting its inverse.) Furthermore, I refer to the
first, second, third, and fourth diagrams, counting from the left.

\begin{proof}
	The prompt implies that the first diagram, at least, is
	commutative; so we know that \(f' = \beta f \alpha \).

	At this point, it might be tempting to immediately right-compose both sides
	of that expression with \(\alpha^{-1}\), to obtain \(f'(\alpha^{-1}) = \beta
	f \alpha(\alpha^{-1})\). Then we could simplify to obtain \(f' \alpha^{-1} =
	\beta f\), and \textit{voil\'{a}!} The second diagram commutes! \dots Right?

	Well, no, not quite. The logic above is missing a crucial step---it first
	assumes that we actually \textit{can} right-compose both sides of \(f' =
	\beta f \alpha \) with \(\alpha^{-1}\). It is true that since an isomorphism
	can always be composed with its inverse, the validity of the composition
	\(\beta f \alpha (\alpha^{-1})\) is trivial. But the validity of \(f'
	(\alpha^{-1})\) is decidedly non-trivial, and this must be proven before the
	logic above can be applied.

	First, it will be useful to explicitly identify the domains and codomains of the
	morphisms included in each diagram, to make further references more concise.
	These can easily be inferred from the diagrams: \(f \colon a \to b; f' \colon a'
	\to b'; \alpha \colon a' \to a;\) and \(\beta \colon b \to b';\) while the
	inverses of each morphism go between the same objects, but with the domain and
	codomain reversed. Now the remainder of the proof becomes almost trivial:

	As stated above, \(\cod(\alpha^{-1}) = \dom(\alpha) = a' = \dom (f')\). So
	\(\dom(f') = \cod(\alpha^{-1})\), which means \(f' \alpha^{-1}\) is a valid
	composition. With that in mind, we are now able to apply the logic quoted in the
	note above to show that \(f' \alpha^{-1} = \beta f\); and this is sufficient to
	show that the second diagram commutes.

	To show that the remaining diagrams commute, we must prove that \(\beta^{-1} f'
	= f \alpha\) and that \(\beta^{-1} f' \alpha^{-1} = f\), for the third and
	fourth diagrams respectively. Again, it is easy to obtain these expressions by
	composing \(\beta^{-1}\) with the expressions we have already determined --
	specifically, by taking the compositions \((\beta^{-1})f' = (\beta^{-1})\beta f
	\alpha = f \alpha\) for the third diagram and \((\beta^{-1})f' \alpha^{-1} =
	(\beta^{-1})\beta f = f\) for the fourth. The 'difficult' part is to show that
	these compositions are valid.

	Fortunately, this is still fairly easy: the validity of \(\beta^{-1} \beta\) is
	trivial, and \(\dom(\beta^{-1}) = \cod(\beta) = b' = \cod(f')\), so \(\beta^{-1}
	f'\) is valid. This means that the compositions mentioned in the previous
	paragraph are valid, and therefore that \(\beta^{-1} f' = f \alpha\) and
	\(\beta^{-1} f' \alpha^{-1} = f\). So the third and fourth diagrams commute.
\end{proof}
\end{document}
