\documentclass[main.tex]{subfiles}
\begin{document}

\settheorem{1}{5}{7}
\begin{definition}
	A functor $\func{F}{C}{D}$ is
	\begin{itemize}
		\item \textbf{full} if for each $x,y\in \cat{C}$, the map $\cat{C}(x,y)\rightarrow\cat{D}(Fx,Fy)$ is surjective;
		\item \textbf{faithful} if for each $x,y\in \cat{C}$, the map $\cat{C}(x,y)\rightarrow\cat{D}(Fx,Fy)$ is injective;
		\item and \textbf{essentially surjective on objects} if for every object $d\in\cat{D}$, there is some $c\in\cat{C}$ such that $d$ is isomorphic to $Fc$.
	\end{itemize}
\end{definition}

\setexercise{1}{5}{11}
\begin{exercise}(For $\Field\mapsto\Ring$)
	Consider the functor $\Field\mapsto\Ring$ (inclusion). Determine whether or not this functor is full, faithful, or essentially surjective. Does it define an equivalence of categories?
\end{exercise}

\begin{proof}
	The inclusion functor $\func{\iota}{\Field}{\Ring}$ is faithful: it must take each morphism in the domain to itself in the codomain and is thus injective. To show it is full, let $\func{f}{x}{y}$ be a field homomorphism in $\Field$. It must take $f(0_x)=0_y$ and $f(1_x)=1_y$. Since we are only concerned with morphisms between objects we know are fields in the domain ($\Field$) of the functor, we know that in the codomain ($\Ring$) every morphism between $\iota x$ and $\iota y$ must also have that $\iota f(0_x) = 0_{\iota x}$ and $\iota f(1_x) = 1_{\iota y}$ (and respect the rest of the ring homomorphism requirements). But then $\iota f$ must be a field homomorphism, and is thus included in $\Field$.
	
	The incusion functor is not essentially surjective on objects however. There is no object in $\Field$ that this functor takes to the zero ring (and the zero ring is unique up to isomorphism). So, the inclusion map from $\Field\mapsto\Ring$ does not define an equivalence of categories.
\end{proof}

\end{document}
