\documentclass[../../main]{subfiles}
\begin{document}
\maketitle

\paragraph{}
\begin{exercise}
	Consider the functors \(\Ab\to\Group\) (inclusion), \(\Ring\to\Ab\)
	(forgetting multiplication), \(\func{(-)^\times}{\Ring}{\Group}\) (taking
	the group of units), \(\Ring\to\Rng\) (inclusion), \(\Field\to\Ring\)
	(inclusion), and \(\Mod{R}\to\Ab\) (forgetful). Determine which functors are
	full, which are faithful, and which are essentially surjective. Do any
	define equivalence of categories? (Warning: A few of these questions conceal
	research-level problems, but they can be fun to think about even if full
	solutions are hard to come by.)
\end{exercise}

\subparagraph{\(\Ab\to\Group\)}
\begin{proof}
	This is a fully faithful functor. For any two groups $x$ and $y$, the
	functor maps the group homomorphisms $f\colon x \rightarrow y$ to
	themselves.  In other words $Ff = f$.  This immediately gives us that the
	functor is faithful, as if $Ff = Fg$, then $f = g$. For it to be full, we
	must confirm that for any groups $x,y \in \msf{Ab}$ that for any $g\colon Fx
	\rightarrow Fy$ we can find $f\colon x \rightarrow y$ such that $Ff = g$.
	But then we note that $g$ is of domain $x$ and codomain $y$ as $F$ is just
	inclusion, and that any homomorphism $g$ between two Abelian groups in the
	category of groups also exists in the category of Abelian groups.  Thus, we
	have the desired surjectivity.

	However, our functor is not essentially surjective on objects.  We know that
	for $c \in \msf{Ab}$, $Fc = c \in\Group$.  For it to be essentially
	surjective, for any $d \in \Group$, we would need to be able to find an $Fc$
	isomorphic to it. But this just means we need to find an Abelian group
	isomorphic to $d$.  That is impossible for any group $d$ that is not
	Abelian, as Abelian groups are only isomorphic to Abelian groups. It thus
	does not define an equivalence of categories, however the Abelian groups are
	a subcategory.
\end{proof}

\end{document}
