\documentclass[main.tex]{subfiles}
\DeclareFontFamily{U}{skulls}{}
\DeclareFontShape{U}{skulls}{m}{n}{ <-> skull }{}
\newcommand{\skull}{\text{\usefont{U}{skulls}{m}{n}\symbol{'101}}}
\begin{document}
	\title{Math 490 HW 3}
	\author{Amarit Matharu}
	\maketitle
	\setexercise{1}{5}{10}
	 \begin{exercise}
	 	Characterize the categories that are equivalent to 
	 	discrete categories. A category that is connected and essentially 
	 	discrete is 
	 	called \textbf{chaotic}.
	 \end{exercise}
	 \begin{proof}
	 	We will show that a category $ \sC $ is equivalent to a discrete category $ \sD $ if and only $ \sC $ is preorder and a groupoid.
	 	Consider any category $ \sC $ that is equivalent to a discrete category 
	 	$ \sD $. By theorem 1.5.9 we have a full, faithful, and essentially 
	 	surjective functor $ F $ from $ \sC $ to $\sD. $ Since $ F $ is both 
	 	full and 
	 	faithful, we have for each $ x,y\IN\ob\sC $ the map $ 
	 	\sC(x,y)\to\sD(Fx,Fy) $ is a bijection. Because $ \sD $ is a discrete 
	 	category we know that $ \sD(Fx,Fy) $ is empty if $ Fx\AND Fy $ 
	 	are distinct or, if they are the same, consists of only the identity 
	 	map. Since $ \sC(x,x)\to \sD(Fx,Fx) $ is a bijection and $ \sD(Fx,Fx) $ 
	 	only contains the identity map we can conclude that $ \sC(x,x) $ also  
	 	only consists of the identity map. Now let $\sC(x,y)$ be inhabited by $ 
	 	f, $ so $ \sD(Fx,Fy) $ is inhabited as well and we must have $ Fx=Fy.$  
	 	Hence there must be exactly one morphism between $ x\AND y\IN C. $ 
	 	Using similar reasoning we can conclude $ \sC(y,x) $ has at most one 
	 	element. Since both $ \sC(x,y) \AND \sC(y,x)$ are mapped to the 
	 	identity of $ Fx $ we must have $fg=gf=1_x .$ Hence between any objects 
	 	$ x\AND y\IN\sC $ $ \sC(x,y) $ has exactly one member or is empty. Since 
	 	every morphism in $ \sC $ is invertible for any two objects $ x\AND 
	 	y\IN\sC $ there is at most one element in the $ \sC(x,y),$ $ \sC $ is 
	 	a groupoid and preorder as desired.
	 	
	 	Conversely consider any category $ \sC $ that is both a groupoid and a 
	 	preorder. For insurance reasons we will work in a universe $ V, $ 
	 	where $ \sC $ is a small category.  
	 	Now look at the skeleton category of $\sC, $ the category whose 
	 	objects are exactly one element from each isomorphism classes (which we obtain by using the axiom of choice, and hence the reason for the insurance policy) of $ \sC,$ denoted 
	 	as  \skull. By definition we know that $ \skull\simeq \sC.$ Because 
	 	$ \sC $ is a groupoid, if $ \sC(x,y) $ is nonempty for any two objects 
	 	$ x\AND y\IN\sC,$ we must have that $ x $ is isomorphic tos $ y$ and 
	 	therefore in the same isomorphism class. Also since $ \sC $ is a 
	 	preorder there is at most one element in $ \sC(x,y).$ So all the 
	 	morphisms of $ \sC $ are collapsed into the identity morphisms of the 
	 	appropriate isomorphism classes. Hence the only morphisms of $ \skull $ 
	 	are the identities of each isomorphism class, so $ \skull $ is discrete 
	 	category. There for $ \sC $ is equivalent to a discrete category and 
	 	this completes the proof.
	 \end{proof}
 
 \end{document}
