\documentclass[../../main]{subfiles}
\begin{document}

\paragraph{}
\begin{exercise}
	 Prove that if $F\colon \sC \rightarrow \Set$ is representable, then $F$
	 preserves monomorphisms, i.e., sends every monomorphism in $\sC$ to
	 an injective function. Use the contrapositive to find a covariant
	 set-valued function defined on your favorite concrete category that is not
	 representable.
\end{exercise}

\begin{proof}

If $F \colon \sC \rightarrow  \Set$ is representable, we have, for some object
$c \in \sC$, a natural isomorphism $\eta\colon F \Rightarrow \sC(c,-)$. We can
represent $\eta$ by the following commutative diagram, for a morphism $f\colon
x\rightarrow y$. We note that $\sC(c,-)(f) = f_*$, where $f_*$ is
post-composition with $f$.
$$
\xymatrix{
Fx
\ar[r]^{Ff}
\ar[d]_{\eta_x}
& Fy
\ar[d]^{\eta_y}
\\
\sC(c,x)
\ar[r]_{f_*}
&\sC(c,y)
}
$$
Since this diagram commutes, we have that $\eta_yFf = f_* \eta_x$.  Also, since
$\eta_y$ is an isomorphism, we know that $Ff = \eta_y^{-1}f_*\eta_x$. Now,
suppose $f$ is a monomorphism. This means that $f_*$ is injective. We know that
$\eta_x$ and $\eta_y^{-1}$ are injective by the defintion of natural
isomorphism. So $Ff$ is in injective, as it is a composition of injective
morphisms. So we see that $F$ preserves monomorphisms.

Now, we note that the contrapostive of this statement says that for a functor
$F\colon \sC \rightarrow \Set$, if $Ff$ is not injective for a monomorphism
$f$, then
$F$ is not representable. Consider the category $\sC_*$ whose objects and
morphisms are $ A =\{0,1\} \AND B = \{0,1,2\} $  and $\{1_A, 1_B, f\}$ respectively, where $f
 \colon A \rightarrow B$ is defined by $f(0)=f(1)= 1.$ (This category and
morphism was previously presented and discussed in exercise 1.6.v.) Because of
the size of our category, we know that $fh = fk$ implies that $h = k = 1_A$, so
$f$ is a monomorphism. But if we consider the functor $F_*\colon \sC_* \rightarrow
\Set$ that includes $\sC_*$ in $\Set$, we see that $Ff = f$ is not injective. So
by the contrapositive of the statement previously proven, $F_*$ is not
representable.
\end{proof}
\end{document}
