\documentclass[main.tex]{subfiles}
\begin{document}

\setexercise{1}{2}{7}
\begin{exercise}
	Regarding a poset \((\sP,\le)\) as a category, define the supremum of a
	subcollection of objects \(A\in\sP\) in such a way that the dual
	statement defines the infimum. Prove that the supremum of a subset of
	objects is unique, whenever it exists, in such a way that the dual proof
	demonstrates the uniqueness of the infimum.
\end{exercise}
\begin{proof}
	Given a subcollection of objects \(A\in\sP\), define an upper bound as
	follows: a object \(u\) is an upper bound of \(A\) if for all objects \(x\)
	in \(A\) there is a morphism \(\func{f}{x}{u}\). Note that this immediately
	gives us a dual notion of a lower bound by considering instead
	\(\sP^\op\). A lower bound of \(A\) in \(\sP\) is an upper bound of \(A\) in
	\(\sP^\op\). In other words an object \(l^\op\) such that for all objects
	\(x^\op\) in \(A\) there is a morphism \(\func{f^\op}{x^\op}{l^\op}\), or
	equivalently \(\func{f}{l}{x}\).

	Letting \(F\) be the collection of all upper bounds of \(A\), we define the
	supremum of \(A\), if it exists, to be a lower bound of \(F\) (as defined
	above) which is contained in \(F\). The condition of containment implies
	uniqueness. Supposing we have two lower bounds \(x\) and \(y\) of \(F\). If
	both are contained in \(F\), then there are maps \(\func{f}{x}{y}\) and
	\(\func{g}{y}{x}\). Since the only endomorphisms in \(\sP\) are identities
	these must be inverses, and because \(\sP\) is a partially ordered set (as
	opposed to just being a preordered set) the only isomorphisms are
	identities. Thus \(x\) and \(y\) are the same object.

	We may thus define the infimum of \(A\) to be its supremum on \(\sP^\op\).
	This time we consider the collection \(I\) of lower bounds \(A\) (the upper
	bounds of \(A\) in \(\sP^\op\)). The infimum is then an upper bound of \(I\)
	which is contained in \(I\) (a lower bound in \(\sP^\op\)). The infimum must
	be unique because it's a supremum in the opposite category, and suprema are
	unique.
\end{proof}
\end{document}

